Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

The part of the paper from this point till the end of Section~\ref{sec:hv:type2} will be devoted to proving the above lemma. This is the most challenging step in settling the general $k$-SJ problem optimally, as we will see in Appendix~\ref{sec:ksj}, where we will prove Theorems~\ref{thm:main-recur} and \ref{thm:main-alg} based on Lemma~\ref{lmm:hv}.

>>>>

The part of the paper from this point till the end of Section~\ref{sec:hv:type2} will be devoted to proving the above lemma. This is the most challenging step in settling the general $k$-SJ problem optimally, as we will see in Section~\ref{sec:ksj}, where we will prove Theorems~\ref{thm:main-recur} and \ref{thm:main-alg} based on Lemma~\ref{lmm:hv}.
